Random Panel Partitions in Surf Competitions: Testing Nationality Bias using Exchangeability

### 2022-10-12 ARTICLE.tex
writing

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}

@@

See KS_stats.jl, KS_stats_conditional.jl
The KS statistic really just bounds on max abs diff is really not compelling given the distribution of residuals. It might make sense to use this pointiwse a bunch.

@@

\subsection{Distributions over measures}
Let:
$\Omega_C = \{(AUS)^{n_A}\otimes(BRA)^{n_B}\otimes(ESP)^{n_E}\otimes(FRA)^{n_F}\otimes(PRT)^{n_P}\otimes(USA)^{n_U}\otimes(ZAF)^{n_Z} \mid n = (n_A,n_B,n_E,n_F,n_P,n_U,n_Z) \in \mathbb{N}^7 \}$ $ = \{Sort(w) \mid w \in l(C)\}$
$\mu$ be a random measure on $\mathscr{P}(\Omega_C)$, i.e. $\mu:\mathscr{P}(\Omega_C)\rightarrow[0,1]$.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{mathtools}

\newcommand{\mathscr}{\mathcal}

@@

%See KS_stats.jl, KS_stats_conditional.jl
The KS statistic really just bounds on max abs diff is really not compelling given the distribution of residuals. It might make sense to use this pointiwse a bunch.

@@

\subsection{Distributions over measures}
Let:
$\Omega_C = \{(AUS)^{n_A}\otimes(BRA)^{n_B}\otimes(ESP)^{n_E}\otimes(FRA)^{n_F}\otimes(PRT)^{n_P}\otimes(USA)^{n_U}\otimes(ZAF)^{n_Z} \mid n = (n_A,n_B,n_E,n_F,n_P,n_U,n_Z) \in \mathbb{N}^7 \}$ $ = \{Sort(w) \mid w \in l(C)\}$
$\mu$ be a random measure on $\mathcal{P}(\Omega_C)$, i.e. $\mu:\mathcal{P}(\Omega_C)\rightarrow[0,1]$.
